---
title: "Writing Great R Code"
output:
  html_document:
    df_print: paged
---

Great R Code - originally referenced here; https://www.safaribooksonline.com/learning-paths/learning-path-introduction/9781491987209/9781491920886-video209185

check out https://www.amazon.co.uk/Code-Complete-Practical-Handbook-Construction/dp/0735619670/ref=sr_1_1?ie=UTF8&qid=1507627980&sr=8-1&keywords=code+complete+2

remember to code for readability!!! Code for robustness

Writing Stylish Code

Use a style guide
decide which naming convention you us
  eg lowercamelcase , UpperCamelCase, lower_under_case AND STICK TO IT!!
  
  go here https://4dpiecharts.com/r-code-style-guide/

```{r loadpackages, echo = TRUE, message = FALSE}
library(sig)
library(assertive)
library(testthat)
library(roxygen2)
library(lattice)
```

## Spacing

Writing the following looks cramped

```{r formula1, echo = TRUE, message = FALSE, eval = FALSE}
y<-sin(2*pi+x)^2

# this looks cramped compared to

y <- sin (2 * pi + x) ^ 2
```

Generally - it is best practice to translate wide code to long code - eg one argument per line and = signs aligned

```{r bwplottest, eval = FALSE}
bwplot(
  decrease ~ treatment,
  OrchardSprays,
  groups              = rowpos,
  panel               = "panel.superimpose"
)

```

## Writing Robust Code
When writing a function you can add a condition that stops the function form outputting gibberish if the wrong data is supplied eg

```{r conffunction, eval = FALSE}
triangular <- function(n)
{
  stopifnot(all(n > 0))
  0.5 * n * (n+1)
}
triangular(c(10, -1))
## ERROR: all(N>0) IS NOT TRUE - this is the actual error message you would get

```
Better however is to use the assertive library

```{r conffunctioncont, eval = FALSE}
triangular <- function(n)
{
    assert_all_are_positive(n)
    0.5 * n * (n+1)
}
triangular(c(10, -1))
```

Assertive has a number of data quality checks too eg email addresses! Not fool proof though

## Testing

There are 2 methods of testing = runit and testthat - testthat is more robust
Here is a basic function

```{r testing_basefunc}
hypotenuse <- function(x,y)
{
  sqrt ( x^ 2 + y ^ 2)
}

hypotenuse(3,4)
```

```{r testing_the_base_func}
test_that("hypotenuse function works with simple inputs", # add comments here to state what the test is supposed to achieve
          {
            actual <- hypotenuse(3,4)
            expected <- 5
            expect_equal(actual, expected)
          }
        ) 
```

